\documentclass[a4paper]{article}
\usepackage[a4paper]{geometry}

\usepackage{CJKutf8}
\usepackage{booktabs}
\usepackage[colorlinks, linkcolor=red]{hyperref}
\begin{document}


\title{Corpra used in our paper}
\maketitle

There are two kinds of corpra used in our paper: Real and fake. The real corpra we used are included in reference. We will introduce the fake corpra in the following content.

\section{Paper generator}
We use SCIgen\cite{PG} to generate random Computer Science research paper.
\section{N-gram generator}
Based on Sinica Corpus, we build the table of Chinese words. The N-gram generator\cite{NG} selects $N$ Chinese characters into one word. After build up a word list, the user can asks these word obey Zipf's distribution or nonZipf distribution like Gussian. 
\section{Mix text}
A text that composed of different books written by different authors is also a fake corpus. We made two different mix text: Newspaper and Mix. The former is the collection of Chinese Time News over the past 10 years, while the latter is mixing of Ref.\cite{Foong}\cite{Yu}\cite{forg}.


\begin{CJK}{UTF8}{bsmi}
\begin{thebibliography}{}
	\bibitem{Moby Dick} Herman Melville. {\it Moby-Dick}. Urbana, Illinois: Project Gutenberg. Retrieved  from \url{https://www.gutenberg.org/ebooks/2701} (2008)
	\bibitem{hobbit} J.R.R. Tolkien. {\it The Hobbit}. ISBN: 0618260307. (2002)
	\bibitem{harry} J.K. Rowling,  Mary GrandPré (Illustrator), Adolfo Muñoz García y Nieves Martín Azofra. {\it Harry Potter and the Prisoner of Azkaban}. ISBN: 9780439655484. (2004)
	\bibitem{scholar} Wu Jingzi. {\it The Scholar} . Retrieved from \url{https://zh.wikisource.org/zh-hant/%E5%84%92%E6%9E%97%E5%A4%96%E5%8F%B2} (2017)
	\bibitem{forg} Mo Yan. {\it Frog}. ISBN: 9787532136766. (2009)
	\bibitem{Einstein} Einstein. {\it Relativität der
		Gleichzeitigkeit}. Retrieved from \url{http://www.mahag.com/srt/1905.php} (1905)
	\bibitem{chopsticks} S.T. Tsai. et al. Acoustic Emission from Breaking a Bamboo Chopstick. Phys. Rev. Lett. 116, 035501 – Published 19 January 2016
	\bibitem{Yu} Yu Guangzhong. {\it Selected Poetry of Yu Guangzhong}. ISBN：9576742730. (2006)
	\bibitem{Xu} Xu Zhimo. {\it Xu Zhimo - Selected Poems}. ISBN：9789861783840. (2016)
	\bibitem{Jin} Jin Yong. {\it Demi-Gods and Semi-Devils}. ISBN: 9789573256748. (1996)
	\bibitem{Foong} Chang Show-Foong. {\it Zhang Xiaofeng Prose Collection}. ISBN：9574441407. (2004)
	\bibitem{PG} Jeremy Stribling, Max Krohn, Dan Aguayo. SCIgen - An Automatic CS Paper Generator.  Retrieved from \url{https://pdos.csail.mit.edu/archive/scigen/} (2017)
	\bibitem{Sinica} Academia Sinica.  Sinica Corpus. Retrieved  from \url{http://godel.iis.sinica.edu.tw/CKIP/engversion/20corpus.htm} (2017)
	\bibitem{NG} Shan-Jyun Wu. Fake Script Vietnamese. Retrieved  from \url{http://godel.iis.sinica.edu.tw/CKIP/engversion/20corpus.htm} (2017)
\end{thebibliography}
\end{CJK}
\end{document}